\documentclass[11pt,a4paper]{article}

% ------------------- PACKAGES -------------------
\usepackage[margin=1.7cm]{geometry}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{titlesec}
\usepackage{ragged2e}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\definecolor{accent}{HTML}{1B5E20} % dark green
\definecolor{lightaccent}{HTML}{4CAF50}

% ------------------- SECTION STYLE -------------------
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}
  {0pt}
  {}
\titlespacing*{\section}{0pt}{10pt}{4pt}

% A green horizontal rule under section titles
\newcommand{\sectionrule}{\vspace{-2pt}\hrule height 1pt \color{accent}\vspace{4pt}}

% ------------------- HELPER COMMANDS -------------------
\newenvironment{entry}[2]{
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    \textbf{#1} & {\small #2} \\
  \end{tabular*}
}{\vspace{2pt}}

\newcommand{\subentry}[1]{\textit{#1}\\[2pt]}

\newenvironment{itemlist}{
  \begin{itemize}[leftmargin=1.5em,itemsep=2pt,topsep=2pt]
}{
  \end{itemize}
}

% ------------------- DOCUMENT -------------------
\begin{document}
\raggedright

% =================== HEADER ===================
{\LARGE\bfseries Spandan Barve}\\[3pt]
{\large\color{accent}Full Stack Blockchain Developer}\\[6pt]

\faEnvelope\hspace{4pt}\href{mailto:contact@marsian.dev}{contact@marsian.dev}
\hspace{10pt}
\faEnvelope[regular]\hspace{4pt}\href{mailto:spandan567@gmail.com}{spandan567@gmail.com}
\hspace{10pt}
\faGithub\hspace{4pt}\href{https://github.com/marsian83}{github.com/marsian83}
\hspace{10pt}
\faLinkedin\hspace{4pt}\href{https://linkedin.com/in/marsian83}{linkedin.com/in/marsian83}
\hspace{10pt}
\faGlobe\hspace{4pt}\href{https://marsian.dev}{marsian.dev}

\vspace{8pt}

% =================== SUMMARY ===================
\section*{Summary}
\sectionrule
Software developer with deep expertise in blockchain, full-stack web development, and open-source contributions. Passionate about privacy, security and minimizing regulatory overreach with technology. Ranked among top teams across global Web3 hackathons.

% =================== EXPERIENCE ===================
\section*{Experience}
\sectionrule

\begin{entry}{Polkadot Blockchain Academy - PBA 7}{Aug 2025 -- Sept 2025}
\end{entry}
\subentry{Polkadot Academy \hfill Bali, Indonesia}
\begin{itemlist}
  \item Graduated from the dApps track at PBA Campus, an in-person blockchain development program with instructors from the Polkadot ecosystem and Parity.
  \item Deep-dived into Polkadot's architecture, Polkadot API, and dApp development with hands-on exercises and mentorship.
  \item Mastered Papi / Polkadot.js tooling and gained extensive knowledge of Polkadot's inner workings, runtime environment, and cross-chain communication (XCMp).
\end{itemlist}

\begin{entry}{Google Summer of Code 2024 -- Project Contributor}{May 2024 -- Sept 2024}
\end{entry}
\subentry{Sugar Labs \hfill Remote}
\begin{itemlist}
  \item Selected among the top 2.7\% of 43{,}984 applicants to develop educational software for the Sugar Labs organisation.
  \item Developed 8 interactive math and logic activities for Sugar, an open-source desktop environment and learning platform aimed at children's educational growth.
  \item Utilized Python, GTK+3, Pygame, and custom modules to create engaging, user-friendly learning activities that support cognitive skill development.
\end{itemlist}

\begin{entry}{Software Architect}{Dec 2023 -- July 2024}
\end{entry}
\subentry{MixR.gg \hfill Remote -- Texas, USA}
\begin{itemlist}
  \item Designed and led the architecture of a scalable e-commerce platform integrating Shopify via Rye.com, supporting community commerce, rewards, and low-fee transactions.
  \item Built a seamless Web3 experience using Particle Network for OAuth-based wallet auth, gasless transactions, and NFT-based loyalty passes with ERC-721 and LayerZero bridging.
  \item Developed a performant backend in Go (Gin) with modular routes for auth, cart, orders, and Stripe sync, including blockchain event handling and admin controls.
\end{itemlist}

\begin{entry}{LFX Mentorship -- Project Contributor}{Sept 2023 -- Dec 2023}
\end{entry}
\subentry{Cloud Native Computing Foundation -- Vitess \hfill Remote}
\begin{itemlist}
  \item Designed and implemented a comprehensive Admin Panel to manage performance benchmarks for Vitess (a scalable MySQL database used by YouTube) using Arewefastyet to automatically detect and prevent performance regressions.
  \item Led a full redesign and rewrite of the web UI, improving user experience and usability for performance monitoring.
  \item Utilized Gin framework for server-side development, with React, TypeScript, and Tailwind CSS on the client-side to deliver a seamless, responsive, and modern interface.
\end{itemlist}

\begin{entry}{Frontend and Tooling Engineer}{Aug 2023 -- Dec 2023}
\end{entry}
\subentry{TalentLayer \hfill Remote}
\begin{itemlist}
  \item Developed a robust SDK and a suite of developer tools to facilitate the creation of hiring marketplaces and talent pools using TalentLayer's open Web3 protocol.
  \item Built a reusable React components library to streamline development and enhance user experience across projects, keeping in mind compatibility across various JavaScript runtimes.
  \item Designed the SDK for fully type-safe interactions with the underlying graph, providing developers with a simplified and abstracted interface for seamless integration.
\end{itemlist}

% =================== PROJECTS ===================
\section*{Projects}
\sectionrule

\begin{entry}{Filosign}{}
\end{entry}
\subentry{Trustless On-Chain E-Signature Platform}
\begin{itemlist}
  \item On-chain e-signature platform replacing platform risk of centralized services with a permanent, verifiable ledger built on F(E)VM and Filecoin Onchain Cloud.
  \item Features irrevocable signatures as permanent blockchain transactions, end-to-end encryption using Kyber KEM, and post-quantum secure signatures using Dilithium.
  \item Built with React 19, Tailwind CSS, and shadcn/ui for the frontend; Solidity smart contracts deployed on Filecoin FVM (FSManager, FSFileRegistry, FSKeyRegistry).
  \item Implements PIN (with Argon2id) + wallet-signature-based HKDF key generation and XChaCha20-Poly1305 encryption; integrates Synapse SDK + FilCDN for decentralized storage and retrieval.
\end{itemlist}

\begin{entry}{Haithe}{}
\end{entry}
\subentry{Decentralized AI Marketplace Ecosystem}
\begin{itemlist}
  \item Decentralized AI marketplace combining blockchain with advanced AI orchestration for a trustless, composable, and monetizable platform.
  \item Enables creation and deployment of AI agents with multi-model support (GPT, Ollama, DeepSeek, etc.) with a marketplace for buying/selling AI components (knowledge bases, tools, prompt sets) and USDT-based transparent payments.
  \item Rust (Actix) based server with Alith agentic framework for AI orchestration on the backend; Solidity smart contracts deployed on Metis Hyperion Testnet.
  \item Features multi-tenant organization system with role-based access control, exposes OpenAI-compatible APIs, and automated creator revenue distribution (pay-per-call system) via smart contracts.
\end{itemlist}

\begin{entry}{JustInsure}{}
\end{entry}
\subentry{Decentralized Insurance Marketplace Platform}
\begin{itemlist}
  \item Enables users to create, manage, and claim insurance policies without intermediaries, enhancing transparency and reducing disputes through blockchain-based smart contracts.
  \item Supports gasless meta transactions for policy-related activities, while ensuring secure client-server communications through ECDSA signatures. Provides an integrated cloud-based Python execution environment (self-hosted) for remote code execution.
  \item Built with React, TypeScript, and Tailwind CSS on the frontend; Deno, Express, and Mongoose on the backend; and Solidity with Hardhat for smart contract development, with integrations like Pinata.cloud and OpenZeppelin for enhanced functionality.
\end{itemlist}

\begin{entry}{PumpFaxt}{}
\end{entry}
\subentry{Token Launchpad}
\begin{itemlist}
  \item Platform for launching ERC20 tokens, utilizing account abstraction and meta transactions to enhance user experience and improve user onboarding.
  \item Uses AMM bonding-curve methodologies for dynamic price determination and virtualLiquidity for price assignment without relying on real liquidity.
  \item Implements data management solutions to efficiently store fast-moving data streams like price history.
  \item Ensures security and compliance by developing smart contracts aligned with the latest OpenZeppelin standards and a custom implementation for meta transactions inspired by the EIP4773 paper.
\end{itemlist}

\begin{entry}{Echo}{}
\end{entry}
\subentry{The All-Encompassing Hub for EduChain}
\begin{itemlist}
  \item Central interface for all on-chain needs for the Open Campus network by Animoca Brands.
  \item Developed a customizable dashboard to display metrics for EDU performance, portfolio, token holdings, and a Proof of Humanity protocol to measure user authenticity based on factors such as Gitcoin score and on-chain activities.
  \item Created a decentralized exchange (DEX) for EduChain using the Uniswap V3 protocol and facilitating cross-chain swaps using LayerZero, including a token launchpad for seamless listing.
  \item Implemented support for various NFT types, including ERC721 NFTs, locked-content NFTs, and on-chain academic records, along with an intuitive NFT marketplace for buying and selling digital assets.
\end{itemlist}

\begin{entry}{OnePanel}{}
\end{entry}
\subentry{Admin Panel as a Service}
\begin{itemlist}
  \item Developed an admin panel as a service for non-technical users to add and manage their application data efficiently, providing developers with the ability to define data structures and schema for their projects.
  \item Implemented secure data handling and access-control mechanisms within the admin panel with exposed API endpoints to enable developers to use the data with their preferred architecture plans.
  \item Built using Golang for microservices and React for the GUI.
\end{itemlist}

% =================== ACHIEVEMENTS ===================
\section*{Achievements}
\sectionrule

\begin{itemlist}
  \item \textbf{Metis HyperHack (2024)} -- Won the hackathon with \textit{Haithe}, a decentralized AI marketplace ecosystem built on Metis L2.
  \item \textbf{Tron Grand HackaTron -- Season 7 (Sept -- Nov 2024)} -- Third prize in the DeFi track and fourth prize in the community track among 1300+ participants with \textit{JustInsure}.
  \item \textbf{Opencampus Educhain Hackathon -- Semester 1 (July -- Aug 2024)} -- 8th prize in the Infra track among 700+ projects and 4500+ participants with \textit{Echo}. Featured in Forbes Web3.
  \item \textbf{Fraxtal Hackathon (May -- July 2024)} -- Third prize of the Mainnet track with \textit{PumpFaxt}.
  \item \textbf{EthOxford (March 2024)} -- Won the main track of Decentralized Social Media and Gaming, along with two sponsor prizes from Solana and Bitso with \textit{Loxel}.
  \item \textbf{Avalanche Frontier Hackathon 2024 (Jan -- March 2024)} -- Stood a winner among 440+ participants and 150+ projects with \textit{Nest}.
  \item \textbf{Web5: Building the Decentralized Web (Jan 2024)} -- Won the Best Empowerment \& Enablement Inspired App among 1500+ participants with \textit{FifthPoll}.
  \item \textbf{EthOxford (Feb 2025)} -- Won the pool prize for the Flare: Enshrined Data Protocols track with \textit{Radio}.
  \item \textbf{Lambda Hack Week (July 2024)} -- Second prize overall from Lambda Week, second prize from Node101, and User Key Management prize from Dora Factory track with \textit{Maci Keychain}.
  \item \textbf{Chainlink Spring Hackathon (April -- June 2023)} -- Chainlink Tech for Good 2nd Prize among 2500+ participants and 500+ projects with \textit{AgroSurance}.
  \item \textbf{EthforAll (Feb 2023)} -- Best Gaming and NFT track by Mantle among 400+ projects with \textit{TrustPoint}.
\end{itemlist}

\end{document}
